### 2024-11-28 Manuscript/supplementaries.tex
added empirical table
Added all results tables

\begin{landscape}
\begin{table}
\scriptsize
\caption{Results of the model scaled metric $\sim$ removal level per stressor (2D)}
\centering
\begin{tabular}[t]{l|c|c|c|c|c|c|c|c}
\hline
  & equalizing slope & equalizing adj.$R^{2}$ & facilitation slope & facilitation adj.$R^{2}$ & filtering slope & filtering adj.$R^{2}$ & competition slope & competition adj.$R^{2}$\\
\hline
Functional evenness\\distances\\ \texttt{FD::dbFD()\$FEve} & 0.017*** & 0.02 & -0.015** & 0.012 & 0.026*** & 0.057 & -0.001 & -0.001\\
\hline
Functional evenness\\dendrogram\\ \texttt{BAT::evenness} & 0.014** & 0.011 & -0.016** & 0.014 & 0.024*** & 0.038 & -0.009* & 0.007\\
\hline
Functional evenness\\hypervolume\\ \texttt{BAT::kernel.evenness} & 0.007 & 0.002 & -0.006 & 0 & 0.03*** & 0.069 & 0.004 & 0\\
\hline
Functional evenness\\probability density\\ \texttt{TPD::REND} & 0.002 & -0.001 & -0.055*** & 0.07 & 0.001 & -0.001 & -0.02*** & 0.048\\
\hline
Rao's quadratic entropy\\distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.185*** & 0.578 & 0.022** & 0.009 & 0.102*** & 0.117 & 0.022** & 0.013\\
\hline
Functional dispersion\\dendrogram\\ \texttt{BAT::dispersion} & 0.08*** & 0.396 & 0.009. & 0.003 & 0.054*** & 0.195 & 0.008* & 0.005\\
\hline
Functional dispersion\\hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.018** & 0.009 & -0.023*** & 0.04 & 0.014* & 0.004 & -0.022*** & 0.048\\
\hline
Divergence\\probability density\\ \texttt{TPD::REND} & 0.066*** & 0.436 & -0.028*** & 0.046 & -0.009. & 0.004 & -0.022*** & 0.038\\
\hline
Alpha diversity\\dendrogram\\ \texttt{BAT::alpha} & 0.227*** & 0.572 & 0.044*** & 0.037 & 0.091*** & 0.155 & 0.002 & -0.001\\
\hline
Functional richness\\convex hull\\ \texttt{BAT::hull.alpha} & -0.09*** & 0.293 & -0.002 & -0.001 & -0.027*** & 0.043 & -0.011* & 0.008\\
\hline
Functional richness\\hypervolume\\ \texttt{BAT::kernel.alpha} & 0.018*** & 0.049 & 0.046*** & 0.179 & 0.004 & 0 & -0.012*** & 0.02\\
\hline
Functional richness\\probability density\\ \texttt{TPD::REND} & 0.09*** & 0.356 & 0.14*** & 0.28 & 0.022*** & 0.037 & -0.009* & 0.005\\
\hline
\end{tabular}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
\scriptsize
\caption{Results of the model scaled metric $\sim$ removal level per stressor (4D)}
\centering
\begin{tabular}[t]{l|c|c|c|c|c|c|c|c}
\hline
  & equalizing slope & equalizing adj.$R^{2}$ & facilitation slope & facilitation adj.$R^{2}$ & filtering slope & filtering adj.$R^{2}$ & competition slope & competition adj.$R^{2}$\\
\hline
Functional evenness\\distances\\ \texttt{FD::dbFD()\$FEve} & 0.054*** & 0.143 & -0.009 & 0.002 & 0.032*** & 0.076 & 0.002 & 0\\
\hline
Functional evenness\\dendrogram\\ \texttt{BAT::evenness} & 0.013* & 0.007 & -0.032*** & 0.092 & 0.015** & 0.012 & -0.002 & 0\\
\hline
Functional evenness\\hypervolume\\ \texttt{BAT::kernel.evenness} & 0.049*** & 0.122 & 0.008 & 0.002 & 0.061*** & 0.194 & 0.018*** & 0.038\\
\hline
Functional evenness\\probability\\ \texttt{TPD::REND} & 0.03*** & 0.135 & -0.01 & 0.002 & 0.024*** & 0.09 & 0.001 & -0.001\\
\hline
Rao's quadratic entropy\\distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.164*** & 0.539 & -0.02** & 0.012 & 0.039*** & 0.023 & -0.002 & -0.001\\
\hline
Functional dispersion\\dendrogram\\ \texttt{BAT::dispersion} & 0.108*** & 0.535 & -0.009** & 0.009 & 0.067*** & 0.258 & 0.012*** & 0.025\\
\hline
Functional dispersion\\hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.064*** & 0.145 & -0.004 & 0.002 & 0.045*** & 0.05 & 0.005* & 0.004\\
\hline
Divergence\\probability density\\ \texttt{TPD::REND} & 0.11*** & 0.52 & -0.03*** & 0.071 & 0.034*** & 0.065 & 0.004 & 0.001\\
\hline
Alpha diversity\\dendrogram\\ \texttt{BAT::alpha} & 0.153*** & 0.393 & 0.059*** & 0.083 & 0.014* & 0.005 & -0.035*** & 0.048\\
\hline
Functional richness\\convex hull\\ \texttt{BAT::hull.alpha} & -0.118*** & 0.517 & 0.013*** & 0.018 & -0.025*** & 0.06 & -0.002 & 0\\
\hline
Functional richness\\hypervolume\\ \texttt{BAT::kernel.alpha} & -0.008** & 0.009 & -0.015*** & 0.016 & -0.006 & 0.002 & -0.001 & -0.001\\
\hline
Functional richness\\probability density\\ \texttt{TPD::REND} & 0.016*** & 0.037 & 0.196*** & 0.535 & 0.014*** & 0.02 & -0.001 & -0.001\\
\hline
\end{tabular}
\end{table}
\end{landscape}

\begin{landscape}
\begin{table}
\scriptsize
\caption{Results of the model scaled metric $\sim$ removal level per stressor (8D)}
\centering
\begin{tabular}[t]{l|c|c|c|c|c|c|c|c}
\hline
  & equalizing slope & equalizing adj.$R^{2}$ & facilitation slope & facilitation adj.$R^{2}$ & filtering slope & filtering adj.$R^{2}$ & competition slope & competition adj.$R^{2}$\\
\hline
Functional evenness\\distances\\ \texttt{FD::dbFD()\$FEve} & 0.039*** & 0.071 & 0.013** & 0.009 & 0.026*** & 0.051 & 0 & -0.001\\
\hline
Functional evenness\\dendrogram\\ \texttt{BAT::evenness} & -0.023*** & 0.041 & -0.038*** & 0.122 & -0.024*** & 0.102 & -0.008*** & 0.056\\
\hline
Functional evenness\\hypervolume\\ \texttt{BAT::kernel.evenness} & -0.055*** & 0.159 & -0.051*** & 0.121 & -0.034*** & 0.093 & -0.007*** & 0.015\\
\hline
Functional evenness\\probability\\ \texttt{TPD::REND} & -0.032*** & 0.134 & -0.118*** & 0.345 & -0.059*** & 0.185 & -0.008*** & 0.03\\
\hline
Rao's quadratic entropy\\distances\\ \texttt{FD::dbFD()\$RaoQ} & 0.088*** & 0.157 & -0.02** & 0.01 & 0.013 & 0.002 & -0.012. & 0.004\\
\hline
Functional dispersion\\dendrogram\\ \texttt{BAT::dispersion} & 0.05*** & 0.166 & -0.022*** & 0.055 & 0.01. & 0.003 & -0.005 & 0.002\\
\hline
Functional dispersion\\hypervolume\\ \texttt{BAT::kernel.dispersion} & 0.035*** & 0.035 & -0.004 & 0.001 & 0.028*** & 0.029 & -0.007** & 0.009\\
\hline
Divergence\\probability density\\ \texttt{TPD::REND} & 0.037*** & 0.121 & -0.029*** & 0.101 & -0.005 & 0 & -0.017*** & 0.041\\
\hline
Alpha diversity\\dendrogram\\ \texttt{BAT::alpha} & 0.03*** & 0.019 & 0.08*** & 0.131 & 0.041*** & 0.028 & -0.041*** & 0.05\\
\hline
Functional richness\\convex hull\\ \texttt{BAT::hull.alpha} & -0.077*** & 0.265 & 0.031*** & 0.09 & -0.009* & 0.006 & 0.002 & -0.001\\
\hline
Functional richness\\hypervolume\\ \texttt{BAT::kernel.alpha} & -0.019** & 0.013 & -0.023*** & 0.017 & -0.02*** & 0.018 & 0.002 & -0.001\\
\hline
Functional richness\\probability density\\ \texttt{TPD::REND} & 0.014** & 0.012 & 0.175*** & 0.574 & 0.08*** & 0.112 & -0.002 & -0.001\\
\hline
\end{tabular}
\end{table}
\end{landscape}

>>>>

\newpage

\subsection{Model results}

\begin{landscape}
\input{Tables/results_model2d.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_model4d.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_model8d.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_empirical.tex}
\end{landscape}

\newpage

\subsection{Average differences between null and focal stressors}

\begin{landscape}
\input{Tables/results_differences2d_1.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences2d_2.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences2d_3.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences2d_4.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences4d_1.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences4d_2.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences4d_3.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences4d_4.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences8d_1.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences8d_2.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences8d_3.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differences8d_4.tex}
\end{landscape}

\begin{landscape}
\input{Tables/results_differencesempirical.tex}
\end{landscape}
